Untitled

### 2017-07-15 PaperCode.Rmd
Summary Function
Created a function to create summary statistics of the BootStrapRES function

#Perform the t-test on the resulting lists
TtestRESgreater <-BootStrapRES %>% map(~ValueTtest(.x))
TtestREStwo.sided <-BootStrapRES %>% map(~ValueTtest(.x, alternative = "two.sided"))
#Tidy results of thejust the ttest
TtestRES2 <- TtestRESgreater %>% map_df(~.x$t.test %>% tidy) %>%
  mutate(LAD = elementnames,
         absdiff = TtestRESgreater %>% map_dbl(~.x$absdiff),
         Percdiff = TtestRESgreater %>% map_dbl(~.x$Percdiff))

#This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
TtestRES2 %>% ggplot(.,aes(x= absdiff, y = Percdiff)) + geom_point() 
TtestRES2 %>% ggplot(.,aes(x= absdiff, y = p.value)) + geom_point()
TtestRES2 %>% ggplot(.,aes(x= Percdiff, y = p.value)) + geom_point()

#Perform ANOVA on the difference between the ratios of the groups on the bootrapped list
ANOVARES <- BootStrapRES %>% 
  map_df(~aov(.x$RatioExvsAct~.x$class) %>% tidy) %>% 
  filter(term != "Residuals") %>%
  select(-term) %>%
  mutate(LAD = elementnames)

WardData <- ls(pattern = "DATA") %>%
  map_df(~eval(parse(text=.x)) %>%
           select(WardLowUsePerc) %>%
        mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
          summarise( maxPerc = max(WardLowUsePerc, na.rm=TRUE),
          minPerc = min(WardLowUsePerc, na.rm=TRUE),
          diffPerc = maxPerc-minPerc,
          LAD = sub("DATA", "", .x)))

skew <- BootStrapRES %>% map_df(~.x %>% group_by(class) %>%
  summarise(skew = mean(RatioExvsAct, na.rm = TRUE)) %>%
  summarise(skew = skewness(skew))
)

Combine1 <- left_join(ANOVARES, TtestRES2, by = "LAD" ) %>% left_join(WardData,by = "LAD" ) %>% bind_cols(skew)

@@

Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = p.value.y)) + geom_point()

#P.value is low if diff perc is over 5%
#Both southwark and Tower of london have concil flat renovation?
#Southwark the Aylesbury estate is being redeveloped making emptyness much higher than expected
#The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
Combine1 %>% ggplot(.,aes(x= diffPerc, y = p.value.y)) + geom_point()

Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y)) + geom_point() +
  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")

#Boring doesn't show anything interesting
Combine1 %>% ggplot(.,aes(x= p.value.x, y = p.value.y, colour =diffPerc>5 )) + geom_point()

Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y, colour =absdiff>0 )) + geom_point()

test <- Combine1 %>%
  select(LAD,p.value.x, p.value.y, absdiff , maxPerc, minPerc,diffPerc, skew)

Combine1 %>% ggplot(.,aes(x= skew, y= p.value.y)) + geom_point()

@@

test <- Combine1 %>% filter(p.value.y>0.05)
```

>>>>

Combine1 <- BootResSummaryData(BootStrapRES)

#This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
Combine1 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()

@@

Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = Ttest.p.value)) + geom_point()

#P.value is low if diff perc is over 5%
#Both southwark and Tower of london have concil flat renovation?
#Southwark the Aylesbury estate is being redeveloped making emptyness much higher than expected
#The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
Combine1 %>% ggplot(.,aes(x= diffPerc, y = Ttest.p.value)) + geom_point()

Combine1 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")

#Boring doesn't show anything interesting
Combine1 %>% ggplot(.,aes(x= p.value.x, y = Ttest.p.value, colour =diffPerc>5 )) + geom_point()

Combine1 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value, colour =absdiff>0 )) + geom_point()

test <- Combine1 %>%
  select(LAD,p.value.x, Ttest.p.value, absdiff , maxPerc, minPerc,diffPerc, skew)

Combine1 %>% ggplot(.,aes(x= skew, y= Ttest.p.value)) + geom_point()

@@

test <- Combine1 %>% filter(Ttest.p.value>0.05)
```
